Objectification Special Studies Analysis

### 2019-03-26 Variable creation.Rmd
Fixed paths and other stuff

#Load packages
```{r}
library(nlme)
library(haven)
library(devtools)
library(psych)
library(mosaic)
library(tidyr)
library(dplyr)
library(irr)
select <- dplyr::select

#set working directory
setwd("/Users/katerinakyuchukova/Downloads/kat/")
```

Load data
```{r}
#clark
clark_measures <- read_spss("Clark College Relationships Data/College_Relationship_Measures_1.sav")
clark_pairwise <- read_spss("Clark College Relationships Data/College_Relationship_Pairwise_1.sav")

#smith
smith <- read_spss("College_Relationship_Dyadic_September_14_2018_12_17.sav")

clark_sentences <- read.csv("sexist sentences/coded_sentences.csv")

#trigrams
trigram_check <- read.csv("Clark College Relationships Data/trigrams/AMELIA_check_trigram_grading.csv")
```

@@

##Write out file to grade
#write.csv(smith_trigrams_long, "/Users/katerinakyuchukova/Downloads/kat/Smith College Relationships Data/trigrams_to_grade.csv", row.names=FALSE)

@@

#Write out csv
#write.csv(smith_sentences_long, "/Users/katerinakyuchukova/Downloads/kat/Smith College Relationships Data/sexist_sentences_for_coding.csv", row.names = FALSE)

#Read in coded sentences, code correlations
kat_codes <- read.csv("/Users/katerinakyuchukova/Downloads/kat/Smith College Relationships Data/kat_recode.csv")

xinyu_codes <- read.csv("/Users/katerinakyuchukova/Downloads/kat/Smith College Relationships Data/xinyu_recode.csv")

@@

Write out cleaned data!
```{r}
write.csv(smith_final, "/Users/katerinakyuchukova/Desktop/ObjectInAction/Cleaned data/smith_final.csv" )
write.csv(clark_final, "/Users/katerinakyuchukova/Desktop/ObjectInAction/Cleaned data/clark_final.csv")
```

>>>>

#Load packages
```{r}
library(nlme)
library(haven)
library(devtools)
library(psych)
library(mosaic)
library(tidyr)
library(dplyr)
library(irr)
select <- dplyr::select
```

Load data
```{r}
#clark
clark_measures <- read_spss("Raw data/Clark College Relationships Data/College_Relationship_Measures_1.sav")
clark_pairwise <- read_spss("Raw data/Clark College Relationships Data/College_Relationship_Pairwise_1.sav")

#smith
smith <- read_spss("Raw data/Smith College Relationships Data/College_Relationship_Dyadic_September_14_2018_12_17.sav")

clark_sentences <- read.csv("Raw data/Clark College Relationships Data/sexist sentences/coded_sentences.csv")

#trigrams
trigram_check <- read.csv("Raw data/Clark College Relationships Data/trigrams/AMELIA_check_trigram_grading.csv")
```

@@

##Write out file to grade
#write.csv(smith_trigrams_long, "Raw data/Smith College Relationships Data/trigrams_to_grade.csv", row.names=FALSE)

@@

#Write out csv
#write.csv(smith_sentences_long, "Raw data/Smith College Relationships Data/sexist_sentences_for_coding.csv", row.names = FALSE)

#Read in coded sentences, code correlations
kat_codes <- read.csv("Raw data/Smith College Relationships Data/kat_recode.csv")

xinyu_codes <- read.csv("Raw data/Smith College Relationships Data/xinyu_recode.csv")

@@

Write out cleaned data!
```{r}
write.csv(smith_final, "ObjectInAction/Cleaned data/smith_final.csv" )
write.csv(clark_final, "ObjectInAction/Cleaned data/clark_final.csv")
```

### 2019-03-26 full analysis file.Rmd
Fixed paths and other stuff

#looking at variables
```{r}
view <- variable_view(clark_measures)
glimpse(clark_measures)
glimpse(clark_pairwise)
names(clark_measures)

variable_view(clark_measures)

@@

#making shit numeric
ix <- 1:39
smith_pair[,ix] <- lapply(smith_pair[,ix], as.numeric)
clark_pair[,ix] <-lapply(clark_pair[,ix], as.numeric)

@@

corr.test(select(samegender_smith, physanx_A, a2pSOO_A, metaSOO_A, authenticity_A, howbody_avg_A, relag_A, careerasp_A, TSO_A, avg_sexism_A, sexism_logel_A))
corr.test(select(samegender_clark, physanx, a2pSOO, metaSOO, authenticity, howbody_avg, relag, careerasp, TSO, avg_sexism, sexism_logel))

corr.test(select(samegender_clark, a2pSOO_A, a2pSOO_P, metaSOO_A, metaSOO_P, howbody_avg_A))
corr.test(select(diffgender_clark, a2pSOO_A, a2pSOO_P, metaSOO_A, metaSOO_P, howbody_avg_A))
corr.test(select(samegender_clark, authenticity_A, careerasp_A, relag_A))

@@

#boxplots
smith_howbody <- smith_final %>%
  select(howbody_1, howbody_2, howbody_3, howbody_avg) %>%
  gather(variable, value, howbody_1:howbody_avg)

clark_howbody <- clark_final %>%
  select(howbody_1, howbody_2, howbody_3, howbody_avg) %>%
  gather(variable, value, howbody_1:howbody_avg)

smith_howbody$value <- as.numeric(smith_howbody$value)
clark_howbody$value <- as.numeric(clark_howbody$value)

>>>>

#looking at variables
```{r}
glimpse(clark_measures)
glimpse(clark_pairwise)
names(clark_measures)
```

@@

#making variables numeric
ix <- 1:39
smith_pair[,ix] <- lapply(smith_pair[,ix], as.numeric)
clark_pair[,ix] <-lapply(clark_pair[,ix], as.numeric)

@@

#corr.test(select(samegender_smith, physanx_A, a2pSOO_A, metaSOO_A, authenticity_A, howbody_avg_A, relag_A, careerasp_A, TSO_A, avg_sexism_A, sexism_logel_A))
#corr.test(select(samegender_clark, physanx, a2pSOO, metaSOO, authenticity, howbody_avg, relag, careerasp, TSO, avg_sexism, sexism_logel))

#corr.test(select(samegender_clark, a2pSOO_A, a2pSOO_P, metaSOO_A, metaSOO_P, howbody_avg_A))
#corr.test(select(diffgender_clark, a2pSOO_A, a2pSOO_P, metaSOO_A, metaSOO_P, howbody_avg_A))
#corr.test(select(samegender_clark, authenticity_A, careerasp_A, relag_A))

@@

#boxplots
#smith_howbody <- smith_final %>%
  #select(howbody_1, howbody_2, howbody_3, howbody_avg) %>%
  #gather(variable, value, howbody_1:howbody_avg)

#clark_howbody <- clark_final %>%
  #select(howbody_1, howbody_2, howbody_3, howbody_avg) %>%
  #gather(variable, value, howbody_1:howbody_avg)

#smith_howbody$value <- as.numeric(smith_howbody$value)
#clark_howbody$value <- as.numeric(clark_howbody$value)
